An RMarkdown template for a preprint recommended by one of the Peer Communities In

### 2024-05-27 PCItemplate-main/manuscript.Rmd
Before instatext

---
title: "An RMarkdown template for a preprint recommended by one of the Peer Communities In"
which_PCI: ecology
# which_PCI MUST BE one of:
# ecology
# evolbiol: Evolutionary Biology
# paleo: Palaeontology
# animsci: Animal Science
# genomics
# archaeo: Archaeology
# zool: Zoology
# mcb: Mathematical & Computational Biology
# fws: Forest & Wood Science
open_data: true #set to false if no open data in article
open_code: true #set to false if no open code in article
author:
  - firstname: Adrien 
    lastname: Tableau
    affiliation: 1
  - firstname: Alain
    lastname: Caizergues
    affiliation: 1,2,a
lastauthor: 
  - firstname: Carol #add last author here if more than one author for proper styling
    lastname: Senior #can be kept empty/deleted otherwise
    affiliation: 1,a
address:
  - code: 1
    address: Some Institute of Technology, Department, Street, City, State, Zip
  - code: 2
    address: Another University Department, Street, City, State, Zip
authorship-notes:
  # - code: a  #delete or keep empty if not needed
    # note: These authors contributed equally to this work. #delete or keep empty if not needed
email: email\@example.com #the "\" before the "@" is needed to escape and compile properly!
abstract: |
  Write your abstract here in a single paragraph, no line breaks. This is the abstract. This is the abstract. This is the abstract. This is the abstract. This is the abstract. This is the abstract. This is the abstract. This is the abstract. This is the abstract. This is the abstract. This is the abstract. This is the abstract. This is the abstract. This is the abstract. This is the abstract. This is the abstract. This is the abstract. This is the abstract. This is the abstract. This is the abstract. This is the abstract. This is the abstract.
keywords:
  - one
  - two
  - optional
  - optional
  - optional

>>>>

---
title: "An RMarkdown template for a preprint recommended by one of the Peer Communities In"
which_PCI: ecology
# which_PCI MUST BE one of:
# ecology
# evolbiol: Evolutionary Biology
# paleo: Palaeontology
# animsci: Animal Science
# genomics
# archaeo: Archaeology
# zool: Zoology
# mcb: Mathematical & Computational Biology
# fws: Forest & Wood Science
open_data: true #set to false if no open data in article
open_code: true #set to false if no open code in article
author:
  - firstname: Adrien 
    lastname: Tableau
    affiliation: 1
  - firstname: Léonard
    lastname: Heinry
    affiliation: 1,2,a
lastauthor: 
  - firstname: Alain #add last author here if more than one author for proper styling
    lastname: Caizergues #can be kept empty/deleted otherwise
    affiliation: 1,a
address:
  - code: 1
    address: Some Institute of Technology, Department, Street, City, State, Zip
  - code: 2
    address: Another University Department, Street, City, State, Zip
authorship-notes:
  # - code: a  #delete or keep empty if not needed
    # note: These authors contributed equally to this work. #delete or keep empty if not needed
email: email\@example.com #the "\" before the "@" is needed to escape and compile properly!
abstract: |
  Write your abstract here in a single paragraph, no line breaks. This is the abstract. This is the abstract. This is the abstract. This is the abstract. This is the abstract. This is the abstract. This is the abstract. This is the abstract. This is the abstract. This is the abstract. This is the abstract. This is the abstract. This is the abstract. This is the abstract. This is the abstract. This is the abstract. This is the abstract. This is the abstract. This is the abstract. This is the abstract. This is the abstract. This is the abstract.
keywords:
  - one
  - two
  - optional
  - optional
  - optional
